---
title: "QMM5"
author: "ISHIKA NISHA"
date: "11/8/2021"
output: html_document
---



```{r}
library(lpSolveAPI)
library(Benchmarking)
```

```{r}
DM1 <-  read.lp("dm1.lp")
DM2 <- read.lp("dm2.lp")
DM3 <- read.lp("dm3.lp")
DM4 <- read.lp("dm4.lp")
DM5 <- read.lp("dm5.lp")
DM6 <- read.lp("dM6.lp")
```

 #values of DM1,DM2,DM3,DM4,DM5,DM6,DM7
 
```{r}
solve(DM1)
get.objective(DM1)
get.variables(DM1)

solve(DM2)
get.objective(DM2)
get.variables(DM2)

solve(DM3)
get.objective(DM3)
get.variables(DM3)

solve(DM4)
get.objective(DM4)
get.variables(DM4)

solve(DM5)
get.objective(DM5)
get.variables(DM5)

solve(DM6)
get.objective(DM6)
get.variables(DM6)

```

```{r}
A <- matrix(c(150,400,320,520,350,320,200,700,1200,2000,1200,700),ncol = 2)
B <- matrix(c(14000,14000,42000,28000,19000,14000,3500,21000,10500,42000,25000,15000),ncol = 2)
colnames(A) <- c("Staff Hours perDay","Supplies perDay")
colnames(B) <- c("Reimbursed Patient-Days","Privately Paid Patient Days")

A
B
```

#A&B) Formulation and performance of DEA analysis under all DEA assumptions of FDH, CRS, VRS,IRS, DRS, and FRH along with the Peers and Lambdas under each of the above assumptions.


```{r}
Analysis.fdh <- dea(A,B,RTS = "fdh")  
Analysis.fdh
peers(Analysis.fdh)
lambda(Analysis.fdh)

Analysis.crs <- dea(A,B,RTS = "crs")  
Analysis.crs
peers(Analysis.crs)
lambda(Analysis.crs)

Analysis.vrs <- dea(A,B,RTS = "vrs")  
Analysis.vrs
peers(Analysis.vrs)
lambda(Analysis.vrs)


Analysis.irs <- dea(A,B,RTS = "irs")
Analysis.irs 
peers(Analysis.irs)
lambda(Analysis.irs)

Analysis.drs <- dea(A,B,RTS = "drs")
Analysis.drs
peers(Analysis.drs)
lambda(Analysis.drs)

Analysis.frh <- dea(A,B,RTS = "add")
Analysis.frh
peers(Analysis.frh)
lambda(Analysis.frh)

```



#D Compare and contrast the above results 

 
dea.plot(A,B,RTS="fdh", main= ("FDH Graph"))
dea.plot(A,B,RTS="crs", main= ("CRS Graph"))
dea.plot(A,B,RTS="vrs", main= ("VRS Graph"))
dea.plot(A,B,RTS="irs",  main= ("IRS Graph"))
dea.plot(A,B,RTS="drs", main= ("DRS Graph"))
dea.plot(A,B,RTS="add", main=("FRH Graph"))

 FDH- All DMs(1,2,3,4,5,6) are effective.

 CRS- DM 1,2,3,and 4 are 100% effective.While, DM5 is 97% effective, and DM6 is   only 86% effective.
 PEERS- The peer value for DM5 are 1,2,and 4,and DM6 are 1,2,and 4.
 LAMBDA- The lambda value for DM6 IS 0.20, 0.08,and o.53 and for DM6 is 0.34,      0.39,and 0.13 

 VRS- DMs (1,2,3,4,5 )are 100% effective. DM 6 is 89% effective.
 PEERS- The peer value for DM6 are 1,2,and 5.
 LAMBDA- The lambda value for DM6 is 0.40, 0.34,and 0.25

 IRS- DMs (1,2,3,4,5 )are 100% effective. DM 6 is 89% effective.
 PEERS- The peer value for DM6 are 1,2,and 5.
 LAMBDA- The lambda value for DM6 is 0.40, 0.34,and 0.25

 DRS- DM 1,2,3,and 4 are 100% effective.While, DM5 is 97% effective, and DM6 is only 86% effective.
 PEERS- The peer value for DM5 are 1,2,and 4,and DM6 are 1,2,and 4.
 LAMBDA- The lambda value for DM6 IS 0.20, 0.08,and o.53 and for DM6 is 0.34, 0.39,and 0.13 

 FRH- All DMs(1,2,3,4,5,6) are effective.